--- 
title: "turkey"
author: "Jonathan Salo"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
biblio-style: apalike
link-citations: yes
description: Notes from Walking the Text trip to Turkey September 2021.
---

# Turkey Trip

```{r eval=FALSE, echo=F}
install.packages("bookdown")
# or the development version
 #devtools::install_github("rstudio/bookdown")
```


```{r include=FALSE,echo=F}
# automatically create a bib database for R packages
#knitr::write_bib(c(
#  .packages(), 'bookdown', 'knitr', 'rmarkdown'
#), 'packages.bib')
```

Notes from [Walking the Text](http://walkingthetestcom) trip to Turkey September 12-24, 2021

- Day 1: Tuesday 9/14
  - Vaclav Museum 
  - Antalya Museum 9/14  
  - Perga Muratpasa.  Harbor. Antalay Museum 10am.  Perga
- Day 2: 9/15 Weds  Gorguorta Mh (outside Yalvac). Museum
  - Colossae????
- Day 3: 9/16 Thurs Denizli Frontinus Gate and Heiropolos (spring). Pamukkale Pools 12pm. Denizli 2pm
  - Laodicea 
- Day 4: 9/17 Fri 
  - Philadelphia
  Tetrapylon Aphordisease Antik Kenti.  Sean Jean Slisesi. Museum with god-fearer inscription. Sebastion reliefs (in museum). Sebastion on site 10am. Huge stadium 11am
  - Aphrodisias city of Marble
- Day 5: 9/18 Sat  Manisa (Vineyardn 9am). Sardis 11am.Artemis Tapinagi 12pm.  Small city park Ragip Bey Mh 5pm
- Day 6: 9/19 Sunday   
  - Ulucamii Mh 9am. 
  - Kurtulus Mh 9:30am. 
  - Theater and temple to Dionysus 10am 
  - Selcuk Mn 12:20pm. 
  - Zafer Mn (Aesculayeon). 
  - Pergamum
  - Smyrna 4pm
- Sabbath
- Day 8: 9/21 Tuesday 
  - Ataturk Mh 10am.  
  - Mt Croessus.
  - Selcuk (Ephesus) museum 1pm. 2 statues of Artemis. 
  - Ephesus Ruins (first day) Pierene
- Day 9: 9/22 Wednesday. 
  - St Jean Kilisesi. Focus on Revelations. 
  - Villas in Ephesus. 
- Day 10: 9/23 Thursday. Didyma. Miletos. Priene?

# Day 1

## Devotion

Who are you? What are you doing here?

Ez 40:4

> And the man said to me, “Son of man, look with your eyes, and hear with your ears, and set your heart upon all that I shall show you, for you were brought here in order that I might show it to you. Declare all that you see to the house of Israel.”

## Alexander the Great

After his death, kingdom was split between four generals:

- Lysimacus - Western Asia Minor
- Seleusus - Eastern Asias Minor (later attacks Lysimicus)
- Ptolemy - Egypt
- Cassander - Macedonia

## Roman Empire

Problem: How to forge a Roman identity across the empire?

### Emporers

- Caesar Agustus
- Tiberius
- Calligula

### History Timeline

Alexander the Great defeats Persians

301BC   Battle of Ipus. After Alexander's death, 4 of his generals divided up his kingdom:

- Seluceus I Nicator controls N Syria 
- Ptolemy I Soter S Syria and Egypt
-
-

## Regions

### Syria

Modern day Palestine (Levant). Province of Syria important to Romans to protect them from the Parthians in the East and from Jewish rebellion in Judea. Quirinius appointed Syria Governor in AD 6^[Wilson, p58]

### Antioch on the Orontes

After death of Alexander the Greek in 306BC, Antigonous I controls Antioch.  After 

### Roman Gods

Artemis

Zeus

Hygei

Apolo

Hermes - Messenger. God of Commerce

Hercules/Paracles

Aesculapyus - God of Medicine.  symbol of snake- who would shed skin and regerate.

### Helenism

Alexander the Great - Was a missionary spreading a message of Helenism

- Changed culture and sports
- Brought an individualistic mentality
- Sex and alcohol to excess



