--- 
title: "turkey"
author: "Jonathan Salo"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
biblio-style: apalike
link-citations: yes
description: Notes from Walking the Text trip to Turkey September 2021.
---

# Turkey Trip

```{r eval=FALSE, echo=F}
install.packages("bookdown")
# or the development version
 #devtools::install_github("rstudio/bookdown")
```


```{r include=FALSE,echo=F}
# automatically create a bib database for R packages
#knitr::write_bib(c(
#  .packages(), 'bookdown', 'knitr', 'rmarkdown'
#), 'packages.bib')
```

Notes from [Walking the Text](http://walkingthetestcom) trip to Turkey September 12-24, 2021

- Day 1: Antalya
- Day 2: 
- Day 3:

- Day 9: Pierene


# Day 1

## Devotion

Who are you? What are you doing here?

Ez 40:4

> And the man said to me, “Son of man, look with your eyes, and hear with your ears, and set your heart upon all that I shall show you, for you were brought here in order that I might show it to you. Declare all that you see to the house of Israel.”

## Roman Empire

Problem: How to forge a Roman identity across the empire?

### Emporers

- Caesar Agustus
- Tiberius
- Calligula

### Roman Gods

Artemis

Zeus

Hygei

Apolo

Hermes - Messenger. God of Commerce

Hercules/Paracles

Aesculapyus - God of Medicine.  symbol of snake- who would shed skin and regerate.

### Helenism

Alexander the Great - Was a missionary spreading a message of Helenism

- Changed culture and sports
- Brought an individualistic mentality
- Sex and alcohol to excess

### Site

[Nymphaeum](https://en.wikipedia.org/wiki/Nymphaeum) - Water souce. Message: Gods and Goddesses bring you your water

Worship of the gods: Underlying concept is that the gods are angry and need to be appeased.

- Christians seen as athiests because they did not worship Roman gods
- Jews were offered exemption to worship of Roman gods by Caesar Augustus
- Jews later told the Romans that Christians were "not one of us", and should not qualify for the exemption.

Question: As a Christian, do you drink the water in the Nymphaem?
### Sarcophagus

Dead buried above ground


